Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle

### 2022-03-28 reportTII-ArticleHIL.tex
Updated Report
Added acknowledgment section
I added an acknowledgment section to the end of the report.

\section{System Architecture}
The overall system architecture of this project consists of six subsystems which are the steering, acceleration, brake, speed, shift, and speed control systems. Each of the six subsystems will be treated as a multiple-input single-output (MISO) system. For each subsystem, every input that is a torque voltage is actually two torque voltage signals, and thus can not be treated as a single input. Also, each subsystem will be treated as a single output system. The brake subsystem is shown to have two outputs but the behaviors of one of the outputs is already known so it will be modeled based on the other output's behavior. 
%
\begin{figure}[htbp]
  \centering
  \missingfigure{Place a high level block diagram including picture of Lexus vehicle that we are modeling}
  \caption{Hexagon Lexus self-driving vehicle showing different subsystems}
  \label{fig:highLevelSystemArchitecture}
\end{figure}

@@

>>>>

\section{System Architecture}
The overall system architecture of this project consists of six subsystems which are the steering, acceleration, brake, speed, shift, and speed control systems. Each of the six subsystems will be treated as a multiple-input single-output (MISO) system. For each subsystem, every input that is a torque voltage is actually two torque voltage signals, and thus can not be treated as a single input. Also, each subsystem will be treated as a single output system. The brake subsystem is shown to have two outputs but the behaviors of one of the outputs is already known so it will be modeled based on the other output's behavior. 
%
\begin{figure}[htbp]
  \centering
  %  \missingfigure{Place a high level block diagram including picture of Lexus vehicle that we are modeling}
  	\includegraphics[height=3cm]{figs/inkscape/carSystemModelOutline}
  \caption{Hexagon Lexus self-driving vehicle showing different subsystems}
  \label{fig:highLevelSystemArchitecture}
\end{figure}

@@

\section*{Acknowledgments}
The authors would like to thank Erik Guetz, Joe Buckner, Sai Chittemsetty, Matt Goben, and AutonomouStuff for their help and collaboration with this project. Without their support this project would never have been possible.
